\chapter{Introduction}

Welcome to my cooky booky.

Example from \verb!xcookybooky! documentation.
\clearpage

% \setBackgroundPicture[x, y, width=\paperwidth-3cm, height, orientation=pagecenter]
% {Images/background}

\setRecipeSizes{
    recipename = \Huge,
    inghead = \small,
    prephead = \small,
}

\begin{recipe}
[ % Optionale Eingaben
	preparationtime = {\unit[1]{h}},
	portion = \portion{5},
	source = R. Gaus
]
{{Mousse au Chocolat}\index{Mousse au Chocolat}}
	
	\graph
	{% Bilder
		small=Images/glass,	% kleines Bild
		big=Images/ingredients % großes (längeres) Bild
	}
	
	\ingredients
	{% Zutaten
		2 Tafeln & dunkle Schokolade\\
				 & (über \unit[70]{\%})\\
		3		 & Eier\\
		\unit[200]{ml} & Sahne\\
		\unit[40]{g} & Zucker\\
		\unit[50]{g} & Butter
	}
	
	\preparation
	{ % Zubereitung
		\step Eier trennen, Eiweiß und Sahne separat steif schlagen. Butter und Schokolade vorsichtig im Wasserbad schmelzen.
		\step Eigelb in einer großen Schüssel mit \unit[2]{EL} heißem Wasser cremig schlagen, den Zucker einrühren bis die Masse hell und cremig ist.
		\step Die geschmolzene Schokolade unterheben, anschließend sofort Eischnee und Sahne unterheben (nicht mit dem Elektro-Mixer!)
		\step Mindestens 2 Stunden im Kühlschrank kalt stellen. Aber nicht zu kalt servieren.
	}
	
	\hint
	{%
		Der Schokoladenanteil kann auch gesenkt werden.
	}

\end{recipe}

\clearpage

\setRecipeSizes{
    recipename = \Huge,
    inghead = \Large,
    prephead = \Large,
}

\begin{recipe}
[ % Optionale Eingaben
	preparationtime = {\unit[10]{min}},
	portion = \portion{1} Lucas portion,
	source = L. Alava Peña
]
{{Salad de Lucas}\index{Salad de Lucas}}
	\introduction
	{
    Salads are a wonderful way to eat your vegetables and take numerous forms, here is Lucas' iteration. 
	}

	\graph
	{% Bilder
		small=Images/glass,	% kleines Bild
		big=Images/ingredients % großes (längeres) Bild
	}

	\ingredients
	{% Zutaten
		2  & Carrots\\
		3/4		 & Cucumber\\
		1/2 & Medium Iceberg lettuce\\
		5-6 & Olives\\
		\unit[80]{g} & Mozzarella\\
		1/4 & Red Bell Pepper\\
        1/4 & Onion\\
        1/4 & Balsamic vinegar\\
        1/4 & Walnut oil
	}
	
	\preparation
	{ % Zubereitung
		\step Wash the vegetables, specifically the red bell peppers, the cucumbers and the iceberg lettuce (ideally using a salad spinner).
		\step[1] Rip the iceberg lettuce apart and put it into the salad bowl. 
		\step Peal the carrots using a peeler (You can also peal the cucumber if you prefer, however, the skin contains some rich nutrients [specifically vitamin K])
		\step Cut the carrots, cucumbers, onions red bell peppers and mozzarella into small pieces.
		\step[1] Put the cuts pieces and the olives into the salad bowl.
		\step Mix the salad, ideally using two wooden spatula. Then whilst mixing, stop mixing and add walnut oil and then balsamic vinegar, then repeat mixing and again a bit of dressing, as to somewhat uniform distribution of dressing.
	}

	\suggestion
	{
	do not steal lucas' salad
	}

\end{recipe}
